{
Here is one way to formulate the problem statement for your thesis on analyzing Solidity code dependencies:

As blockchain platforms and smart contract usage continue to grow, there is an increasing need to ensure
the security, reliability, and efficiency of Solidity smart contract code.
However, understanding complex Solidity code logic, dependencies, and potential risk
exposure remains a significant challenge.
Manual code reviews are time-consuming, error-prone, and rely heavily on auditor expertise.
At the same time, current software analysis tools lack
customizable queries and visibility into low-level code properties and relationships vital for effective audits.

This thesis addresses the need for more granular and automated analysis of Solidity smart contract
dependencies and code properties through a custom query system.
The key problem is developing a methodology
and toolset to construct a detailed program dependence graph of Solidity code elements and enable relevant
customizable queries against this graph.
Specific research questions include:

How can Solidity source code be parsed into a program dependence graph representation encompassing key code properties and relationships?

What query capabilities and interfaces will allow flexible and useful automated analysis of the dependency graph?

How can the graph queries identify security vulnerabilities, compliance issues, optimization opportunities and other critical software quality attributes?

Does the graph-based query approach provide superior auditing and debugging capabilities compared to current analysis solutions?

By investigating these research questions and developing an automated, graph-based query system for Solidity analysis, this thesis aims to enhance smart contract security, efficiency, and development practices in the blockchain ecosystem.

Please feel free to modify or enhance this problem formulation as needed to best reflect your specific thesis goals and the issues you aim to address.
}